---
title: "2"
author: "Alec Lepe"
date: "09/07/2018"
output: 
  html_document:
    keep_md: true
---
```{r setup, include = FALSE}
#install.packages("R")
library("data.table")
library("tidyverse")
knitr::opts_chunk$set(fig.width = 10, fig.length=10, fig.asp = 1/3,  message=FALSE)
fig.path = "~/Figures"
```

### URL
https://github.com/lepealec/MSDS-6306-First-Case-Study.git

### Data description.

### Load and preview data
``` {r load data}
setwd("~/MSDS-6306-First-Case-Study/Guidlines")

beers=fread("beers.csv")
beers
breweries=fread("breweries.csv")
breweries
```


### How many breweries are the per state?
By state,
```{r breweries per state by state}
ct_brew=table(breweries[["State"]])
ct_brew[sort(names(ct_brew))]
breweries %>% ggplot(aes(x=State)) + geom_bar()+xlab("State")+ylab("Count") + 
  scale_y_continuous(name="Count", labels = scales::comma) +
  ggtitle("Brewery Count by State \nBy State")+theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
```{r breweries per state by rank}
ct_brew[order(ct_brew)]
breweries[order(breweries[["State"]]),]
names(ct_brew[order(ct_brew)])

breweries %>% ggplot( aes(x=reorder(State,State,
                     function(x)-length(x)))) + geom_bar()+xlab("State")+ylab("Count") + 
  scale_y_continuous(name="Count", labels = scales::comma) +
  ggtitle("Brewery Count by State \nBy Rank")+theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

Here we can see Colorado (CO), California (CA), and Michigan (MI) have the most breweries with 47, 39, and 32 breweries respectively.

Contrastly, Washington DC (DC), North Dakota (ND), South Dakota (SD), and West Virginia (WV) have the fewest breweries: 1 per state.

```{r total breweries}
nrow(breweries)
```

There are a total of 558 breweries listed in the data set.

``` {r merge data sets}
colnames(breweries)[colnames(breweries)=="Brew_ID"]="Brewery_id"
colnames(breweries)[colnames(breweries)=="Name"]="Brewery_Name"
colnames(beers)[colnames(beers)=="Name"]="Beer_Name"
combined_data=merge(beers,breweries,by="Brewery_id")
nrow(breweries)
nrow(combined_data)==nrow(beers)
```
First six observations
``` {r head}
head(combined_data)
```
Last six observations
``` {r tail}
tail(combined_data)
```
Sum of NA's per column
``` {r sum of NA}
apply(combined_data,2,function(x) sum(is.na(x)))
```

